Pillar 1 - Sequential Pattern Mining

### 2019-01-24 Pillar 1 - Sequential Pattern Mining.Rmd
starting grade addition cbind

probabilities_manipulated <- d_transcript %>%
  select(-Course, -Year_numerical,-Period,-`Number Repeated Attempt`,-`Academic Year`)%>% #remove this before expanding grades
  mutate(Round_grade= round(Grade,0))
```

##Puting students into take and not take. 
```{r}

#this df has 731,676 rows:
test <- expand.grid(`Student ID`= unique(d_transcript$`Student ID`),`Course ID`= unique(d_course$`Course ID`)) %>%
  left_join(d_transcript, by=c("Course ID", "Student ID")) %>%
  select(`Course ID`, `Student ID`, Grade, Year_numerical, Period) %>%
  mutate(
    take_course = case_when(
      is.na(Grade)  ~ FALSE,
      T             ~ TRUE
      ),
    PFN = case_when(
      is.na(Grade)  ~ "not",
      Grade >= 5.5  ~ "pass",
      Grade < 5.5   ~ "fail"
      )
    )

>>>>

probabilities_manipulated <- d_transcript %>%
  transmute(tmp_id=paste(`Student ID`,`Course ID`,Year_numerical,Period,`Number Repeated Attempt`,sep="_"),
            Round_grade= round(Grade,0))
student_set <- unique(probabilities_manipulated$tmp_id)

for student %in% student_set

##Puting students into take and not take. 
```{r}
#This df has 731,676 rows:
test <- expand.grid(`Student ID`= unique(d_transcript$`Student ID`),`Course ID`= unique(d_course$`Course ID`)) %>%
  left_join(d_transcript, by=c("Course ID", "Student ID")) %>%
  select(`Course ID`, `Student ID`, Grade, Year_numerical, Period) %>%
  mutate(
    take_course = case_when(
      is.na(Grade)  ~ FALSE,
      T             ~ TRUE
      ),
    PFN = case_when(
      is.na(Grade)  ~ "not",
      Grade >= 5.5  ~ "pass",
      Grade < 5.5   ~ "fail"
      )
    )
